A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-28 paper/paper.Rnw
modified abstract

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

>>>>

\begin{abstract}
Currently, to assess similarity in forensic shoeprint analysis, examiners must manually identify and label features in images of shoe prints or outsoles. In this paper, we discuss an algorithm for automatically labeling shoe outsole images using the same feature space examiners use: a set of features based on geometric shapes such as circles, stars, and quadrilaterals. The automatic labeling algorithm performs well on images with unambiguous shapes and moderate color contrast, though some systematic errors arise from the physical similarities of geometric shapes. Additional improvements may be realized by modifying the labeling scheme to reduce feature overlap and by preprocessing the images to improve contrast. This new approach represents a significant improvement to the current manual classification of footwear tread patterns, and could be integrated into current matching databases to reduce the amount of time examiners spend on data entry.
\end{abstract}
